---
title: "P8105 HW1 cmh2275"
output: github_document
---

# Problem 1

```{r}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```
## Description of Penguins Dataset

* The Penguins data set contains the following variables: `r ls(penguins)`.
* The Penguins dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.
* The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm.

## Bill Length vs Flipper Length Scatterplot 
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```
## Saving Scatterplot 
```{r}
ggsave ("hw1_billvsflipper_scatterplot.png")
```

# Problem 2 

## Create dataframe
```{r}
hw1prob2_df = tibble(
  norm_samp = rnorm(10),
  norm_samp_pos = norm_samp > 0, 
  vec_char = letters[1:10], 
  vec_factor = factor(rep_len(c ("low", "med", "high"),10)), 
)
```

## Take mean of variables - attempt 1

* The mean of norm_samp is `r mean(pull(hw1prob2_df, norm_samp))`.
* The mean of norm_samp_pos is `r mean(pull(hw1prob2_df, norm_samp_pos))`.
* The mean of vec_char is `r mean(pull(hw1prob2_df, vec_char))`.
* The mean of vec_factor is `r mean(pull(hw1prob2_df, vec_factor))`.


## Convert variables 
```{r, results = "hide"}
as.numeric(pull(hw1prob2_df, norm_samp_pos))
as.numeric(pull(hw1prob2_df, vec_char))
as.numeric(pull(hw1prob2_df, vec_factor))

```

## Take mean of variables - attempt 2

* The mean of norm_samp is `r mean(pull(hw1prob2_df, norm_samp))`.
* The mean of norm_samp_pos is `r mean(pull(hw1prob2_df, norm_samp_pos))`.
* The mean of vec_char is `r mean(pull(hw1prob2_df, vec_char))`.
* The mean of vec_factor is `r mean(pull(hw1prob2_df, vec_factor))`.